### 2019-06-11 doc/chapters/trying_verify_checktx.tex
fixed title
Added No Inflation Property.
changed some lines

\chapter{Trying to Verify the no Inflation Property}
\label{chap:verify_check}

@@

To return a Future does not make sense, since the implementing constructor calls either Future.successfull or Future.fromTry which returns an already resolved Future.
This might be for future purposes.

@@

\section{Fixing a Bug in Bitcoin-S}

>>>>

\chapter{Trying to Verify the No Inflation Property}
\label{chap:verify_check}

@@

The return type Future does not make sense here, since the implementing constructor calls either Future.successfull or Future.fromTry which returns an already resolved Future.
This might be for future purposes.

@@

\section{Fixing a Bug in Bitcoin-S}
\label{sec:bugfix}
